### 2012-12-03 inst/examples/policycosts/figure4.Rmd
figure4 run on farm

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor=element_line(colour="transparent"))
theme_set(theme_notebook)
```

@@

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````

@@

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="figure4/")
```

``` {r}
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
c2 <- seq(0, 20, length.out = 40)
```

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- lapply(penaltyfns, function(penalty){
  sfLapply(c2, function(c2)
      optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                   profit, delta, reward, penalty = penalty(c2))
  )
})
````

@@

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sfLapply(c2, function(c2){
  effort_penalty = function(x,h) c2 * h / x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = none, 
                        effort_penalty)
})
dat <- cbind(policies, quad)
````
